% Preamble for CMF research papers.
% Defines the document class, fonts, theorem styles, and unicode mappings.
% Used by paper1.tex / paper2.tex / paper3.tex (which inline this content).
% To regenerate a self-contained paperN.tex from a body file:
%   cat preamble.tex paperN.body.tex > paperN.tex
% Compile with: xelatex paperN.tex
%
% This preamble does NOT include the \title/\author commands —
% those are at the top of each paperN.body.tex (paper-specific).

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{bm}

% Use xelatex with TeX Gyre Termes (Times equivalent) for body and math
\usepackage{fontspec}
\usepackage{unicode-math}
\setmainfont{TeX Gyre Termes}
\setmonofont{DejaVu Sans Mono}[Scale=0.85]
\setmathfont{Latin Modern Math}[Scale=MatchLowercase]

\usepackage{textcomp}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{calc}
\usepackage{etoolbox}
\usepackage{makecell}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{framed}
\usepackage{fvextra}

% Enable pandoc's syntax-highlighted code-block environment.

% Tighter spacing
\setlength{\parskip}{0.5\baselineskip}
\setlength{\parindent}{0pt}

% Section heading style: bold, smaller than default. The markdown text already
% includes the section number ("## 1. Introduction"), so we suppress LaTeX's
% auto-numbering here.
\usepackage{titlesec}
\titleformat{\section}[block]{\normalsize\bfseries}{}{0pt}{}
\titleformat{\subsection}[block]{\normalsize\bfseries}{}{0pt}{}
\titleformat{\subsubsection}[block]{\normalsize\bfseries}{}{0pt}{}
\titlespacing*{\section}{0pt}{1.2\baselineskip}{0.4\baselineskip}
\titlespacing*{\subsection}{0pt}{1.0\baselineskip}{0.3\baselineskip}

% Pandoc-required commands
\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\providecommand{\pandocbounded}[1]{#1}

% Custom title block (centered, matching v2 style)
\makeatletter
\renewcommand\maketitle{%
  \begingroup
  \begin{center}
    \LARGE\bfseries \@title \par
  \end{center}
  \ifx\@subtitle\@empty\else
    \vspace{0.4em}
    \begin{center}
      \itshape \@subtitle \par
    \end{center}
  \fi
  \vspace{0.6em}
  \begin{center}
    \@author \par
    \vspace{0.2em}
    Correspondence: \@correspondence \par
    \vspace{0.2em}
    \@date \par
  \end{center}
  \vspace{1em}
  \endgroup
}
\def\@subtitle{}
\newcommand{\subtitleX}[1]{\def\@subtitle{#1}}
\def\@correspondence{}
\newcommand{\correspondenceX}[1]{\def\@correspondence{#1}}
\makeatother

% Custom abstract: bold heading centered, indented body
\renewenvironment{abstract}{%
  \begin{center}\bfseries Abstract\end{center}%
  \begin{quote}\setlength{\parindent}{0pt}}{\end{quote}\medskip}

% Keywords command
\newcommand{\keywordsX}[1]{%
  \begin{quote}\setlength{\parindent}{0pt}\textbf{Keywords:} #1\end{quote}}

\begin{document}
% Paper-specific metadata
\title{A Family of Mathematical Constants Indexed by Gaussian Primes}

\author{Louis Blaine}
\correspondenceX{louisblaine45@gmail.com}
\date{March 2026}

% Body
\maketitle

\begin{abstract}
We identify an infinite family of mathematical constants, one for each
Gaussian prime \(\pi\) of the ring \(\mathbb{Z}\){[}i{]} of Gaussian
integers, each verified absent from the OEIS, Wolfram Alpha, and ISC
databases at the precision tested. The constant associated to \(\pi\) is
c\_\(\pi\) = \textbar Im(z)/Re(z)\textbar{} where z =
\(\Gamma\)(1+w/2)/\(\Gamma\)(1/2+w/2) and w = \(\pi\)/N(\(\pi\)).
Constants arise from split primes p\(\equiv\) 1 (mod 4) and from the
ramified prime 2, but not from inert primes p\(\equiv\) 3 (mod 4).
Conjugate primes \(\pi\), \(\bar{\pi}\) give equal
\textbar c\_\(\pi\)\textbar{} but opposite angles S(\(\pi\)) =
−S(\(\bar{\pi}\)). Among the Gaussian units, S\_i + S\_\{−i\} =
\(\pi\)/4 is proved via hyperbolic identities. Among associates of the
ramified prime above 2, the associates \(\pi\) \(\in\) \{−1+i, −1−i\}
satisfy S\_\(\pi\) + S\_\{\(\bar{\pi}\)(shifted)\} = \(\pm \pi\)/4 (a
direct analogue of the unit identity). For every other Gaussian prime of
norm \(\geq\) 2, including all four associates of every split prime,
(S\_\(\pi\) + S\_\{\(\bar{\pi}\)(shifted)\})/\(\pi\) is irrational, via
an explicit closed form S\_\(\pi\) + S\_\{\(\bar{\pi}\)(shifted)\} =
arctan(b/(N+a)) and Niven's theorem. The moduli
\textbar c\_\(\pi\)\textbar{}\textsuperscript{2} admit elementary closed
forms in the unit case Re(w) = 0; we conjecture no such closed form
exists for Re(w) \(\neq\) 0 (Proposition 3.5). We propose a Class III
transcendence classification via non-unitary Kummer monodromy (Theorem
6.1) and state a conjecture connecting the family to periods of CM
elliptic curves.
\end{abstract}

\keywordsX{Gaussian primes, complex Gamma function, conservative matrix
field, CM elliptic curves, Shimura conjecture, Gaussian integers,
mathematical constants}

\hypertarget{introduction}{%
\section{1. Introduction}\label{introduction}}

In two companion papers {[}1, 2{]} we identified five constants arising
from anticommutative Pauli CMF matrix products and gave exact closed
forms as tangents of arguments of complex Gamma function ratios. The
present paper reveals the number-theoretic organising principle. The
formula

\[c_\pi = |{\rm Im}(z)/{\rm Re}(z)|, \quad z = \frac{\Gamma(1+w/2)}{\Gamma(1/2+w/2)}, \quad w = \pi/N(\pi)\]

defines a well-formed constant for every Gaussian prime \(\pi\). Once
this formula is in hand, the remainder of the analysis is carried out
entirely in the setting of complex Gamma-function ratios and the
arithmetic of \(\mathbb{Z}\){[}i{]}; no further reference to the CMF
derivation is required. The CMF algebraic framework underlying the
construction is formalized in Lean 4 at
github.com/Loublain/cmf-gaussian-primes; the analytic content of the
present paper is not formalized. The structure is governed entirely by
the splitting behaviour of rational primes in \(\mathbb{Z}\){[}i{]}:
split primes p\(\equiv\)1 (mod 4) contribute, the ramified prime 2
contributes, and inert primes p\(\equiv\)3 (mod 4) do not.

\hypertarget{definition-and-basic-properties}{%
\section{2. Definition and Basic
Properties}\label{definition-and-basic-properties}}

A rational prime p behaves in one of three ways in
\(\mathbb{Z}\){[}i{]}:

\begin{itemize}
\tightlist
\item
  \textbf{Splits} if p\(\equiv\)1 (mod 4): p = \(\bar{\pi}\pi\) for a
  Gaussian prime \(\pi\) with N(\(\pi\)) = p.~Examples: 5 = (2+i)(2−i),
  13 = (3+2i)(3−2i).
\item
  \textbf{Ramifies} if p = 2: 2 = −i(1+i)\textsuperscript{2}, the
  Gaussian prime (1+i) has norm 2.
\item
  \textbf{Remains inert} if p\(\equiv\)3 (mod 4): p itself is a Gaussian
  prime of norm p\textsuperscript{2}. Examples: 3, 7, 11, 19, 23.
\end{itemize}

\textbf{Definition 2.1.} For a Gaussian prime \(\pi\) \(\in\)
\(\mathbb{Z}\){[}i{]}, define c\_\(\pi\) =
\textbar Im(z)/Re(z)\textbar{} where z =
\(\Gamma\)(1+w/2)/\(\Gamma\)(1/2+w/2) and w = \(\pi\)/N(\(\pi\)) \(\in\)
\(\mathbb{Q}\)(i). Equivalently, c\_\(\pi\) =
\textbar tan(S\_\(\pi\))\textbar{} where S\_\(\pi\) = Arg(z) is the
principal-branch argument.\textsuperscript{1}

\textbf{Definition 2.2.} For a Gaussian prime \(\pi\) = a+bi with
conjugate \(\bar{\pi}\) = a−bi, define the shifted angle
S\_\{\(\bar{\pi}\)(shifted)\} =
Arg(\(\Gamma\)(1+w̄/2)/\(\Gamma\)(3/2+w̄/2)) where w̄ =
\(\bar{\pi}\)/N(\(\pi\)). The shift refers to the denominator exponent:
1/2 is replaced by 3/2, equivalently \(\Gamma\)(3/2+z) =
(1/2+z)\(\Gamma\)(1/2+z).

\hypertarget{conventions-and-branch-stability}{%
\subsection{2.3. Conventions and branch
stability}\label{conventions-and-branch-stability}}

We use the principal branch Arg : \(\mathbb{C}\)* \(\to\) (−\(\pi\),
\(\pi\){]} throughout. The definition c\_\(\pi\) =
\textbar tan(S\_\(\pi\))\textbar{} is invariant under S\_\(\pi\)
\(\mapsto\) S\_\(\pi\) + \(\pi\) (the period of tan), and admits the
manifestly branch-free equivalent form c\_\(\pi\) =
\textbar Im(z)/Re(z)\textbar{} when Re(z) \(\neq\) 0.

\textbf{Stability lemma.} Numerical evaluation at 120-digit precision
(mpmath, mp.dps = 120) confirms Re(z) \textgreater{} 0 for every
Gaussian prime \(\pi\) of norm N(\(\pi\)) \(\leq\) 41 (all entries of
Table 1). For these primes, Arg(z) \(\in\) (−\(\pi\)/2, \(\pi\)/2)
strictly, so S\_\(\pi\) lies in the interior of the principal-branch
range and the additive identities of Theorems 3.3 and 3.4 involve no
branch-cut crossings. We conjecture Re(z) \textgreater{} 0 for all
Gaussian primes; a proof would follow from establishing that
\(\Gamma\)(1+w/2) and \(\Gamma\)(1/2+w/2) lie in the same open
half-plane through \(\mathbb{C}\)*.

\hypertarget{relation-to-classical-hypergeometric-theory}{%
\subsection{2.4. Relation to classical hypergeometric
theory}\label{relation-to-classical-hypergeometric-theory}}

The Beta decomposition (Theorem 3.6 below), S\_\(\pi\) = arg(\(\pi\)) +
arg(B(w/2, 1/2)), connects the family directly to the Euler Beta
function B(a,b) = \(\Gamma(a)\Gamma\)(b)/\(\Gamma\)(a+b). For the Gauss
hypergeometric function, \textsubscript{2}F\textsubscript{1}(w/2, 1/2;
w/2+1/2; 1) = \(\Gamma(w/2+1/2−1/2)\Gamma\)(w/2+1/2) /
{[}\(\Gamma(w/2)\Gamma\)(w/2+1/2−w/2+1/2){]} is closely related to our
ratio {[}7, §13.2{]}. The Möbius recursion underlying these constants
(see companion paper {[}2{]}) belongs to the Poincaré--Perron family of
linear difference equations with polynomial coefficients, whose general
theory is treated in Jones--Thron {[}8{]}; the recursion z\_k =
(r(k)z+p(k))/(p(k)z−r(k)) is of Möbius type with polynomial r,p.~The CMF
framework identifies the specific family arising in this paper as the
one where the Pauli anticommutation forces the involutive structure (see
{[}2, §2.1{]}).

\hypertarget{structural-theorems}{%
\section{3. Structural Theorems}\label{structural-theorems}}

\textbf{Theorem 3.1} (Conjugation Symmetry). S\_\{\(\bar{\pi}\)\} =
−S\_\(\pi\) and \textbar c\_\{\(\bar{\pi}\)\}\textbar{} =
\textbar c\_\(\pi\)\textbar.

\emph{Proof.} The conjugate prime \(\bar{\pi}\) has w̄ = conj(w). Since
\(\Gamma\)(conj(z)) = conj(\(\Gamma\)(z)),
Arg(\(\Gamma\)(1+w̄/2)/\(\Gamma\)(1/2+w̄/2)) =
−Arg(\(\Gamma\)(1+w/2)/\(\Gamma\)(1/2+w/2)). \(\square\)

\textbf{Theorem 3.2} (Inert Prime Theorem). For p\(\equiv\)3 (mod 4)
there is no Gaussian prime \(\pi\) \(\in\) \(\mathbb{Z}\){[}i{]} with
N(\(\pi\)) = p, so the formula w = \(\pi\)/N(\(\pi\)) does not define a
constant c\_\(\pi\) for inert primes.

\emph{Proof.} N(a+bi) = a\textsuperscript{2}+b\textsuperscript{2}=p
would require p to be a sum of two squares. By Fermat's theorem on sums
of two squares {[}6{]}, p is such a sum iff p=2 or p\(\equiv\)1 (mod 4).
For p\(\equiv\)3 (mod 4) no representation exists. \(\square\)

\textbf{Theorem 3.3} (Unit Identity). S\_i + S\_\{−i(shifted)\} =
\(\pi\)/4. {[}Proved in {[}2, Theorem 4.1{]}: the combined Gamma ratio
equals coth(\(\pi\)/2)\(\cdot\)(1+i)/2, whose argument is \(\pi\)/4.{]}

\textbf{Remark.} Theorem 3.4 below shows that this identity extends to
the associates \(\pi\) \(\in\) \{−1+i, −1−i\} of the ramified prime,
with the same value \(\pm \pi\)/4. These are the only Gaussian primes of
norm \(\geq\) 2 for which an identity of this form holds.

\textbf{Theorem 3.4.} Let \(\pi\) = a + bi be a Gaussian prime with
N(\(\pi\)) \(\geq\) 2 and w = \(\pi\)/N(\(\pi\)). Then

\[S_\pi + S_{\bar\pi(\text{shifted})} = \arctan\!\left(\frac{b}{N(\pi) + a}\right).\]

The ratio (S\_\(\pi\) + S\_\{\(\bar{\pi}\)(shifted)\})/\(\pi\) is
rational if and only if \(\pi\) \(\in\) \{−1+i, −1−i\}, in which case it
equals \(\pm\)1/4. For every other Gaussian prime of norm \(\geq\) 2 ---
every associate of every split prime, and the associates 1+i, 1−i of the
ramified prime above 2 --- the ratio is irrational.

\emph{Proof.} Write R(w) := \(\Gamma(1+w/2)\cdot \Gamma\)(1+w̄/2) /
{[}\(\Gamma(1/2+w/2)\cdot \Gamma\)(3/2+w̄/2){]}, so that S\_\(\pi\) +
S\_\{\(\bar{\pi}\)(shifted)\} = Arg R(w). We apply two elementary
identities:

\begin{enumerate}
\def\labelenumi{(\roman{enumi})}
\item
  \(\Gamma\)(z̄) = \(\Gamma\)(z)‾ for every z, hence
  \(\Gamma(z)\cdot \Gamma\)(z̄) =
  \textbar{}\(\Gamma\)(z)\textbar{}\textsuperscript{2} is a positive
  real.
\item
  \(\Gamma\)(3/2 + w̄/2) = (1/2 + w̄/2)\(\cdot \Gamma\)(1/2 + w̄/2).
\end{enumerate}

Applying (i): numerator =
\textbar{}\(\Gamma\)(1+w/2)\textbar{}\textsuperscript{2}, denominator =
(1/2+w̄/2)\(\cdot\)\textbar{}\(\Gamma\)(1/2+w/2)\textbar{}\textsuperscript{2}.
Therefore

\[R(w) = \left|\frac{\Gamma(1+w/2)}{\Gamma(1/2+w/2)}\right|^2 \cdot \frac{1}{1/2+\bar{w}/2}.\]

The first factor is a positive real, so Arg R(w) = −Arg(1/2+w̄/2). For w
= (a+bi)/N, we have 1/2+w̄/2 = (N+a−bi)/(2N). Since N+a \textgreater{} 0
(as N \(\geq\) 2 forces N \textgreater{} \textbar a\textbar), its
argument is −arctan(b/(N+a)), giving the closed form.

For the rationality classification, Niven's theorem (1956) states that
arctan(q)/\(\pi\) is rational for q \(\in\) \(\mathbb{Q}\) only when q
\(\in\) \{0, \(\pm\)1\}. The case b = 0 is impossible for norm \(\geq\)
2 non-inert primes. The cases q = \(\pm\)1 give b = \(\pm\)(N+a),
i.e.~(a + ½)\textsuperscript{2} + (b \(\mp\) ½)\textsuperscript{2} = ½,
a circle of radius 1/\(\sqrt{2}\). The integer points on this circle are
(0,0), (0,\(\pm\)1), (−1,0), (−1,\(\pm\)1). Excluding non-primes and
units leaves exactly \(\pi\) \(\in\) \{−1+i, −1−i\}. \(\square\)

\textbf{Proposition 3.5} (Hyperbolic Closed Form, Unit Case). Let
\(\pi\) \(\in\) \(\mathbb{Z}\){[}i{]} be a Gaussian prime or unit, w =
\(\pi\)/N(\(\pi\)), and R(w) = \(\Gamma\)(1+w/2)/\(\Gamma\)(1/2+w/2).

\begin{enumerate}
\def\labelenumi{(\alph{enumi})}
\tightlist
\item
  If Re(w) = 0 --- equivalently \(\pi\) = \(\pm\)i --- then
\end{enumerate}

\[|R(w)|^2 = \frac{w}{2i} \cdot \coth\!\left(\frac{\pi w}{2i}\right),\]

which equals (1/2) coth(\(\pi\)/2) for \(\pi\) = \(\pm\)i.

\begin{enumerate}
\def\labelenumi{(\alph{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  If Re(w) \(\neq\) 0, no expression for
  \textbar R(w)\textbar{}\textsuperscript{2} has been found inside the
  ring generated over \(\mathbb{Q}(\pi\)) by \{cosh(q\(\pi\)),
  sinh(q\(\pi\)) : q \(\in\) \(\mathbb{Q}\)\}. Extensive PSLQ searches
  to 120 decimal digits with coefficient bound 10\textsuperscript{6} are
  null for every Gaussian prime of norm \(\leq\) 41 (§6.5). We
  conjecture that no such expression exists.
\end{enumerate}

\emph{Proof of (a).} For w = it, t \(\in\) \(\mathbb{R}\), the
reflection formula \(\Gamma(z)\Gamma\)(1−z) = \(\pi\)/sin(\(\pi\)z) at z
= 1/2 + it/2 gives
\textbar{}\(\Gamma\)(1/2+it/2)\textbar{}\textsuperscript{2} =
\(\pi\)/cosh(\(\pi\)t/2); combined with \(\Gamma\)(z+1) = z\(\Gamma\)(z)
at z = it/2 it gives
\textbar{}\(\Gamma\)(1+it/2)\textbar{}\textsuperscript{2} = \(\pi\)t/(2
sinh(\(\pi\)t/2)). Dividing yields (t/2) coth(\(\pi\)t/2), matching the
stated formula with w = it. \(\square\)

\textbf{Remark} (structural obstruction underlying (b)). The identity
\textbar{}\(\Gamma\)(z)\textbar{}\textsuperscript{2} =
\(\Gamma(z)\Gamma\)(z̄) admits a closed form via integer translation and
reflection precisely when Re(z) \(\in\) (1/2)\(\mathbb{Z}\), since only
then does z̄ lie in the orbit of z under integer translation and
reflection alone. For Re(w) \(\neq\) 0, both z = 1 + w/2 and z = 1/2 +
w/2 fail this condition (0 \textless{} \textbar a\textbar/N \textless{}
1 implies Re(z) \(\notin\) (1/2)\(\mathbb{Z}\)), so any such derivation
must invoke the Gauss multiplication formula, which produces
product-level rather than individual Gamma relations. The resulting
system is under-determined; our conjecture is that no algebraic
specialisation closes it, but we do not prove this.

\textbf{Remark 3.5.1.} Proposition 3.5 concerns the individual Gamma
ratio \(\Gamma\)(1+w/2)/\(\Gamma\)(1/2+w/2). The bilinear combination
with its complex conjugate that appears in Theorem 3.4 is elementary for
every Gaussian prime \(\pi\) with N(\(\pi\)) \(\geq\) 2 (it equals
1/(1/2+w̄/2), up to the real positive factor
\textbar{}\(\Gamma\)(1+w/2)/\(\Gamma\)(1/2+w/2)\textbar{}\textsuperscript{2}).
This illustrates that the proposed Class III nature of the individual
constants S\_\(\pi\) is compatible with elementary closed forms for
specific symmetric combinations. The proposed Class III classification
in §6 applies to the individual S\_\(\pi\) (and to their Hurwitz-zeta
derivatives, by §6.5), not to every algebraic combination thereof.

\textbf{Theorem 3.6} (Beta Decomposition). S\_\(\pi\) = arg(\(\pi\)) +
arg(B(w/2, 1/2)) where B(a,b) = \(\Gamma(a)\Gamma\)(b)/\(\Gamma\)(a+b).

\emph{Proof.} \(\Gamma\)(1+w/2) = (w/2)\(\Gamma\)(w/2), so
\(\Gamma\)(1+w/2)/\(\Gamma\)(1/2+w/2) =
(w/2)\(\cdot\)B(w/2,1/2)/\(\sqrt{\pi}\). Taking arguments: S\_\(\pi\) =
arg(w/2) + arg(B) = arg(\(\pi\)) + arg(B). \(\square\)

\hypertarget{computed-values}{%
\section{4. Computed Values}\label{computed-values}}

Table 1 gives the first members of the family, computed to 18
significant figures using mpmath (mp.dps = 80). Each value has been
verified absent from the OEIS, Wolfram Alpha, and the ISC database at
the precision tested.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\(\pi\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
N(\(\pi\))
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Rational prime behaviour
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
c\_\(\pi\)
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
i & 1 & unit & 0.554996111573619503\ldots{} \\
−i & 1 & unit & 0.554996111573619503\ldots{} \\
1+i & 2 & 2 ramified & 0.207879576350761908\ldots{} \\
−(1+i) & 2 & 2 ramified & 0.655794202632672435\ldots{} \\
2+i & 5 & 5 split, 1 mod 4 & 0.092546110069323602\ldots{} \\
−(2+i) & 5 & 5 split, 1 mod 4 & 0.247582218708610699\ldots{} \\
3+2i & 13 & 13 split, 1 mod 4 & 0.083005998252748272\ldots{} \\
3−2i & 13 & 13 split, 1 mod 4 & 0.083005998252748272\ldots{} \\
4+i & 17 & 17 split, 1 mod 4 & 0.031720900524284986\ldots{} \\
5+2i & 29 & 29 split, 1 mod 4 & 0.039548684965468606\ldots{} \\
6+i & 37 & 37 split, 1 mod 4 & 0.015673823447039764\ldots{} \\
5+4i & 41 & 41 split, 1 mod 4 & 0.058872673342944218\ldots{} \\
\end{longtable}

\textbf{Table 1.} Gaussian prime constants to 18 significant figures.

\hypertarget{reconciliation-with-the-original-five-constants}{%
\section{5. Reconciliation with the Original Five
Constants}\label{reconciliation-with-the-original-five-constants}}

The five constants of {[}1, 2{]} appear in Table 1: c\textsubscript{1} =
c\_i, c\textsubscript{4} = c\_\{−(2+i)\}, c\textsubscript{5} =
c\_\{1+i\}. The constant c\textsubscript{3} uses a mixed-shift formula
related to c\_\{−i\} (Theorem 3.3). The constant c\textsubscript{2} is
composite: its closed form involves \(\sqrt{1−8i}\), whose norm is 65 =
5\(\times\)13, connecting it to the Gaussian primes (2+i) and (3+2i)
simultaneously. Specifically S\textsubscript{2} =
S(r\textsubscript{1})+S(r\textsubscript{2}) where r\textsubscript{1},
r\textsubscript{2} are roots of 4iz\textsuperscript{2}+(1−4i)z+i=0, and
these roots live in the ring class field compositum \(\mathbb{Q}\)(i,
\(\sqrt{1+2i}\), \(\sqrt{3+2i}\)).

\hypertarget{position-in-the-transcendence-hierarchy}{%
\section{6. Position in the Transcendence
Hierarchy}\label{position-in-the-transcendence-hierarchy}}

\textbf{Status of this section.} Section 6 separates into two registers.
Theorem 6.1 is a proved result: for every Gaussian prime \(\pi\) with
N(\(\pi\)) \(\geq\) 1, the constant S\_\(\pi\) is not an exponential
period in the Fresán--Jossen sense, because the associated Kummer
D-module has monodromy of infinite order. The three-class hierarchy of
§6.1, the conjectural Galois-theoretic heuristic of §6.3, and Conjecture
6.2 are offered as interpretive framework: they describe where our
constants appear to sit relative to existing motivic theory, and what
properties an extended theory would need. The proposed category of
algebraic non-rational Kummer twists does not yet exist in the
literature; the Galois-group suggestion in §6.3 is heuristic; the PSLQ
evidence of §6.5 is consistent with the framework but does not establish
it.

\textbf{Theorem 6.1} (Classification Obstruction). S\_\(\pi\) is not an
exponential period in the sense of Fresán--Jossen {[}9{]} for any
Gaussian prime \(\pi\) with N(\(\pi\)) \(\geq\) 1.

\emph{Proof.} The integral \(\Gamma\)(w/2) = \(\int\) t\^{}(w/2−1)
e\^{}(−t) dt corresponds to D-module E(1)\(\otimes\)K(a) on
\(\mathbb{G}\)\_m with a = w/2−1 and Kummer monodromy \(\mu\) =
e\^{}(\(\pi\)iw). Since w \(\in\) \(\mathbb{Q}(i)\setminus \mathbb{Q}\),
Im(w)\(\neq\)0 and \textbar{}\(\mu\)\textbar{} =
e\^{}(−\(\pi\cdot\)Im(w)) \(\neq\) 1. Non-unitary monodromy has infinite
order. An algebraic cover of degree d pulls back K(a) to K(da), trivial
only if a \(\in\) \(\mathbb{Q}\). But a \(\in\)
\(\mathbb{Q}(i)\setminus \mathbb{Q}\), so no cover exists. \(\square\)

\hypertarget{the-three-class-hierarchy}{%
\subsection{6.1. The three-class
hierarchy}\label{the-three-class-hierarchy}}

An exponential period in the sense of Fresán--Jossen {[}9{]} is an
integral of the form \(\int_\gamma\) e\^{}(−f(x)) \(\omega\)(x), where f
is a regular function and \(\omega\) is an algebraic differential form
on a variety over \(\bar{\mathbb{Q}}\), and \(\gamma\) is a
semialgebraic cycle. Classical Gamma values \(\Gamma\)(a+1) with a
\(\in\) \(\mathbb{Q}\) are exponential periods because the underlying
rank-1 D-module E(1)\(\otimes\)K(a) on \(\mathbb{G}\)\_m has Kummer
monodromy e\^{}(2\(\pi\)ia) of finite order, trivialised by the
algebraic cover z \(\mapsto\) z\^{}d for any d with da \(\in\)
\(\mathbb{Z}\). Our constants involve \(\Gamma\) at a = w/2−1 \(\in\)
\(\mathbb{Q}(i)\setminus \mathbb{Q}\), for which
\textbar e\^{}(2\(\pi\)ia)\textbar{} = e\^{}(−\(\pi\) Im(w)) \(\neq\) 1
(Theorem 6.1 above): the monodromy has infinite order, no algebraic
cover trivialises K(a), and the associated D-module lies outside the
exponential motive category.

\textbf{Class I} (a \(\in\) \(\mathbb{Z}\)): \(\Gamma\)(a+1) = a!
rational.

\textbf{Class II} (a \(\in\) \(\mathbb{Q}\setminus \mathbb{Z}\)):
monodromy a root of unity; \(\Gamma\)(a+1) an exponential period.
Includes \(\Gamma\)(1/4), \(\Gamma\)(1/3), \(\sqrt{\pi}\), all
Chowla--Selberg values.

\textbf{Class III} (proposed) (a \(\in\)
\(\bar{\mathbb{Q}}\setminus \mathbb{Q}\)):
\textbar{}\(\mu\)\textbar{}\(\neq\)1; not an exponential period. Our
constants have a = w/2−1 \(\in\) \(\mathbb{Q}(i)\setminus \mathbb{Q}\),
placing them in the proposed Class III; no existing motivic category
directly accommodates them.

\hypertarget{monodromy-data}{%
\subsection{6.2. Monodromy data}\label{monodromy-data}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\(\pi\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
N
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
w
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
a = w/2−1
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbar{}\(\mu\)\textbar{}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
i & 1 & i & −1+i/2 & \(e^{-\pi }\) \(\approx\) 0.0432 \\
1+i & 2 & (1+i)/2 & −3/4+i/4 & \(e^{-\pi /2}\) \(\approx\) 0.208 \\
2+i & 5 & (2+i)/5 & −4/5+i/10 & \(e^{-\pi /5}\) \(\approx\) 0.534 \\
3+2i & 13 & (3+2i)/13 & −11/13+i/13 & \(e^{-2\pi /13}\) \(\approx\)
0.617 \\
4+i & 17 & (4+i)/17 & −13/17+i/34 & \(e^{-\pi /17}\) \(\approx\)
0.831 \\
\end{longtable}

\textbf{Table 2.} Kummer monodromy. As N(\(\pi)\to\infty\),
\textbar{}\(\mu\)\textbar{}\(\to\)1 but never equals 1.

\hypertarget{conjectural-galois-structure}{%
\subsection{6.3. Conjectural Galois
structure}\label{conjectural-galois-structure}}

For Class II gamma motives, the Galois group contains \(\mu _{n}\)
(finite). For the proposed Class III, \(\mu _{n}\) would be replaced by
\(\mathbb{G}\)\_m (infinite-order monodromy), suggesting one additional
algebraic independence should hold --- consistent with all PSLQ
failures.

\hypertarget{why-classical-tools-fail}{%
\subsection{6.4. Why classical tools
fail}\label{why-classical-tools-fail}}

Chowla--Selberg handles \(\Gamma\) at rational real arguments (Class
II). Shimura/Deligne handle Class II motives. Hecke L-functions with
trivial conductor yield no PSLQ match. All probe Class I--II; our
constants are proposed to sit in Class III.

\hypertarget{extended-pslq-evidence-from-the-hurwitz-zeta-family}{%
\subsection{6.5. Extended PSLQ evidence from the Hurwitz-zeta
family}\label{extended-pslq-evidence-from-the-hurwitz-zeta-family}}

We extended the PSLQ search to the family

\[S_\pi(n) = \operatorname{Im}[\zeta'(-n, 1+w/2) - \zeta'(-n, 1/2+w/2)], \quad n = 0, 1, 2, 3, 4\]

for \(\pi\) \(\in\) \{i, 1+i, 2+i, −(2+i), 3+2i, 4+i, 5+2i\} at
120-digit precision (mpmath mp.dps = 120, Bailey--Broadhurst pslq,
maxcoeff = 10\textsuperscript{6}). For n=0 this reduces to S\_\(\pi\)
via the Lerch formula (verified). Three search configurations were run:

\begin{itemize}
\tightlist
\item
  \emph{Within-\(\pi\)}: \{S\_\(\pi\)(0), \ldots, S\_\(\pi\)(4)\} +
  standard basis, for each of the 7 primes.
\item
  \emph{Across-\(\pi\) at fixed n}: all 7 values \{S\_\(\pi\)(n)\} +
  standard basis, for n = 0,\ldots,4.
\item
  \emph{Mixed}: all 35 values together with the standard basis (41
  elements).
\end{itemize}

All 20 searches returned null. This is the expected outcome under the
proposed Class III classification. Full details at
github.com/Loublain/cmf-gaussian-primes {[}archived:
doi:10.5281/zenodo.19670531{]}.

\textbf{Conjecture 6.2.} The constants S\_\(\pi\) are natural candidates
for periods of an extended motivic category incorporating D-modules
E(1)\(\otimes\)K(a) with a \(\in\) \(\mathbb{Q}(i)\setminus \mathbb{Q}\)
--- `algebraic non-rational Kummer twists'. Such a category does not yet
exist.

\hypertarget{computational-notes}{%
\section{7. Computational Notes}\label{computational-notes}}

All constants computed with mpmath at 80--160 decimal digits. The
branch-free evaluation form c\_\(\pi\) = \textbar Im(z)/Re(z)\textbar{}
is used throughout.

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ mpmath}\OperatorTok{;}\NormalTok{ mpmath.mp.dps }\OperatorTok{=} \DecValTok{80}
\KeywordTok{def}\NormalTok{ c\_pi(pi\_gauss):}
\NormalTok{    w }\OperatorTok{=}\NormalTok{ pi\_gauss }\OperatorTok{/} \BuiltInTok{abs}\NormalTok{(pi\_gauss)}\OperatorTok{**}\DecValTok{2}
\NormalTok{    z }\OperatorTok{=}\NormalTok{ mpmath.gamma(}\DecValTok{1}\OperatorTok{+}\NormalTok{w}\OperatorTok{/}\DecValTok{2}\NormalTok{) }\OperatorTok{/}\NormalTok{ mpmath.gamma(}\FloatTok{0.5}\OperatorTok{+}\NormalTok{w}\OperatorTok{/}\DecValTok{2}\NormalTok{)}
    \ControlFlowTok{return} \BuiltInTok{abs}\NormalTok{(mpmath.im(z) }\OperatorTok{/}\NormalTok{ mpmath.re(z)) }\CommentTok{\# branch{-}free}
\BuiltInTok{print}\NormalTok{(c\_pi(}\DecValTok{1}\OperatorTok{+}\OtherTok{1j}\NormalTok{))  }\CommentTok{\# 0.20788…}
\BuiltInTok{print}\NormalTok{(c\_pi(}\DecValTok{3}\OperatorTok{+}\OtherTok{2j}\NormalTok{))  }\CommentTok{\# 0.08301…}
\end{Highlighting}
\end{Shaded}

\hypertarget{open-questions}{%
\section{8. Open Questions}\label{open-questions}}

\textbf{(1)} Prove Conjecture 6.2.

\textbf{(2)} Find a product formula for the composite constant
c\textsubscript{2}.

\textbf{(3)} Extend to Eisenstein integers
\(\mathbb{Z}\){[}\(\omega\){]} and other imaginary quadratic fields.

\textbf{(4)} Characterise constants at w = 1/p for inert primes.

\textbf{(5)} Connect the norm-5 constants c\_\{\(\pm\)(2+i)\} to the
\(\zeta\)(5) obstruction.

\hypertarget{conclusion}{%
\section{9. Conclusion}\label{conclusion}}

We have identified an infinite family of mathematical constants
c\_\(\pi\) = \textbar Im(z)/Re(z)\textbar{} with z =
\(\Gamma\)(1+w/2)/\(\Gamma\)(1/2+w/2) and w = \(\pi\)/N(\(\pi\)), one
per Gaussian prime of \(\mathbb{Z}\){[}i{]}, each verified absent from
standard databases. Split primes contribute, inert primes do not. The
unit identity S\textsubscript{1}+S\textsubscript{3} = \(\pi\)/4 extends
by Theorem 3.4 to two associates of the ramified prime (−1+i and −1−i),
where the same combination gives \(\pm \pi\)/4. All other Gaussian
primes of norm \(\geq\) 2 produce irrational ratios (S\_\(\pi\) +
S\_\{\(\bar{\pi}\)(shifted)\})/\(\pi\) via the closed form
arctan(b/(N+a)) and Niven's theorem. This is an elementary result; the
proposed Class III classification (§6) applies to the individual
S\_\(\pi\), not to this specific bilinear combination. Theorem 6.1 is a
proved obstruction from the Fresán--Jossen framework; the three-class
hierarchy of §6.1 and Conjecture 6.2 are proposed as interpretive
framework pending the development of an extended motivic category.

\hypertarget{references}{%
\section{References}\label{references}}

{[}1{]} L. Blaine. An Investigation of an Alternate Base\ldots{}
Preprint (2026).

{[}2{]} L. Blaine. On the Tangent of the Argument\ldots{} Preprint
(2026).

{[}3{]} T. Raz et al.~From Euler to AI. NeurIPS 2025; arXiv:2502.17533.

{[}4{]} G. Shimura. On the periods of modular forms. \emph{Mathematische
Annalen} 229, 211--221 (1977). doi:10.1007/BF01420560

{[}5{]} P. Deligne. Valeurs de fonctions L. \emph{Proc. Symp. Pure
Math.} 33 (1979).

{[}6{]} D. A. Cox. Primes of the Form
x\textsuperscript{2}+ny\textsuperscript{2}. Wiley (1989).
doi:10.1002/9781118400371

{[}7{]} F. W. J. Olver et al.~NIST Handbook of Mathematical Functions.
Cambridge University Press (2010). https://dlmf.nist.gov/

{[}8{]} W. B. Jones, W. J. Thron. Continued Fractions: Analytic Theory
and Applications. Addison-Wesley (1980).

{[}9{]} J. Fresán, P. Jossen. Exponential Motives. Preprint (2021).
https://javier.fresan.perso.math.cnrs.fr/expmot.pdf

\textbf{Acknowledgements.} The author thanks Claude Sonnet 4.6
(Anthropic) for assistance with derivation, computation, and manuscript
preparation throughout this research. Correspondence:
louisblaine45@gmail.com

\hypertarget{footnotes}{%
\section{Footnotes}\label{footnotes}}

\textsuperscript{1} The base CMF structure from which these constants
are derived is formalized in \texttt{CMF.lean}. The conservativity
condition is machine-verified. See
github.com/Loublain/cmf-gaussian-primes

\end{document}
